### 2017-10-02 TF-vldb2018/sec-tsimAlg.tex

In this section, we first study the pattern satisfiability problem for team formation, then introduce two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.

% with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for \warn{strong simulation}~\cite{MaCFHW14}.

@@

			\vspace{-4ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \grouprec}
	\label{alg-grouprec}
	\vspace{-3ex}
\end{figure}

>>>>

%In this section, we first study the pattern satisfiability problem for team formation, then introduce two optimization techniques, and finally we present our  batch algorithm for top-$k$ team formation.

In this section, we develop a batch algorithm for top-$k$ team formation.
We first study the pattern satisfiability problem for team simulation, then introduce two optimization techniques, and finally we present our batch algorithm.
% with one novel feature and two optimizations, \ie pattern satisfiability check, and incremental computing for radius varied balls and density based filtering optimization, compared with traditional algorithms for \warn{strong simulation}~\cite{MaCFHW14}.

@@

			\vspace{-4ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \grouprec}
	\label{alg-grouprec}
	\vspace{-4ex}
\end{figure}

### 2017-10-02 TF-vldb2018/subsec-Qinc.tex

We present algorithm \incp to handle pattern updates $\Delta P$, followed the steps in Section~\ref{subsec-framework}, and
an early return optimization technique for \incp.
%Note that for any $h$-fragmentation ${\cal P}_h$ of $P$, $|{\cal P}_h|$ = $|P|$.

@@

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule \vspace{-2ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} \= $P$, $h$-fragmentation ${\cal P}_{h}$, $G$, integers $r$ and $k$, $\Delta P$, and\\
				\>auxiliary structures $\tilde{M}(P,G)$, \fb, \bfc and \upl.\\
				{\sl Output:\/} Top-$k$ perfect subgraphs for $P \oplus \Delta P$ in $G$.\\
				\sstab \bcc \hspace{1ex} \= $L_{k}$ := $\emptyset$;\\
				\icc \> \affballsx\ :=  $\identifyaffball({\cal P}_h, \Delta P, \fb, \bfc)$;\\
				\icc \> Sort \affballsx by $\ball{}[\kw{den}]$ in non-ascending order;\\
				\icc \> \For \Each $\ball{[v,r]}$ in \affballsx \Do\quad/* non-ascending order */\\
				\icc \> \hspace{3ex} \= \If $|L_{k}| \geq k$ \And $\ball{[v,r]}[\kw{den}] \leq \density{L_{k}[k]}$ \Then \\
				\icc \>\>\hspace{2ex} \= \bf{Output} $L_{k}[0:k-1]$. /* early-return optimization*/\\
				%/* Running in background after returning top-$k$ results for $\Delta P$ */\\
				\icc \>\>$\incmatch(M(P_{fi},\ball{[v,r]}),\ball{[v,r]}, \Delta P_{fi})$ $(i\in[1,h])$;\\
				\>\> /* runs in the background */\\
				\icc \>\> $S_{G_s} := \comb(\bigcup_{i\in [1, h]}M(P_{fi},\ball{[v,r]}), \ball{[v,r]}, C\oplus \Delta C)$;\\
				\icc \>\> Insert the set of perfect subgraphs in $S_{G_s}$ into $L_{k}$;\\
				\icc \> \Return $L_{k}[0:k-1]$.
				%\icc \>\> \If $|L_{k}| < k$ or $\kw{den}(G_s) > \density{L_{k}[k]}$ \Then\\
				%\icc \>\>\hspace{2ex} \= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$.
				%\icc \hspace{-0.2ex}/*b*\hspace{-0.6ex}/\>\>Update the record of $\ball{[v,r]}$ in \fb;
			}
			\vspace{-2.5ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \incp} \label{alg-optInc}
	\vspace{-4ex}
\end{figure}

>>>>

We present algorithm \incp to handle pattern updates $\Delta P$, following the steps in Section~\ref{subsec-framework}, and
an early return optimization technique for \incp.
%Note that for any $h$-fragmentation ${\cal P}_h$ of $P$, $|{\cal P}_h|$ = $|P|$.

@@

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule \vspace{-2ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} \= $P$, $h$-fragmentation ${\cal P}_{h}$, $G$, integers $r$ and $k$, $\Delta P$, and\\
				\>auxiliary structures $\tilde{M}(P,G)$, \fb, \bfc and \upl.\\
				{\sl Output:\/} Top-$k$ perfect subgraphs for $P \oplus \Delta P$ in $G$.\\
				\sstab \bcc \hspace{1ex} \= $L_{k}$ := $\emptyset$;\\
				\icc \> \affballsx\ :=  $\identifyaffball({\cal P}_h, \Delta P, \fb, \bfc)$;\\
				\icc \> Sort \affballsx by $\ball{}[\kw{den}]$ in non-ascending order;\\
				\icc \> \For \Each $\ball{[v,r]}$ in \affballsx \Do\quad/* non-ascending order */\\
				\icc \> \hspace{3ex} \= \If $|L_{k}| \geq k$ \And $\ball{[v,r]}[\kw{den}] \leq \density{L_{k}[k-1]}$ \Then \\
				\icc \>\>\hspace{2ex} \= \bf{Output} $L_{k}[0:k-1]$. /* early-return optimization*/\\
				%/* Running in background after returning top-$k$ results for $\Delta P$ */\\
				\icc \>\>$\incmatch(M(P_{fi},\ball{[v,r]}),\ball{[v,r]}, \Delta P_{fi})$ $(i\in[1,h])$;\\
				\>\> /* runs in the background */\\
				\icc \>\> $S_{G_s} := \comb(\bigcup_{i\in [1, h]}M(P_{fi},\ball{[v,r]}), \ball{[v,r]}, C\oplus \Delta C)$;\\
				\icc \>\> Insert the set of perfect subgraphs in $S_{G_s}$ into $L_{k}$;\\
				\icc \> \Return $L_{k}[0:k-1]$.
				%\icc \>\> \If $|L_{k}| < k$ or $\kw{den}(G_s) > \density{L_{k}[k]}$ \Then\\
				%\icc \>\>\hspace{2ex} \= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$.
				%\icc \hspace{-0.2ex}/*b*\hspace{-0.6ex}/\>\>Update the record of $\ball{[v,r]}$ in \fb;
			}
			\vspace{-2.5ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \incp} \label{alg-optInc}
	\vspace{-4ex}
\end{figure}

### 2017-10-02 TF-vldb2018/subsec-auxstr.tex

Auxiliary structures fall into two classes:
maintain partial matches and handle pattern incremental computing. Consider an $h$-fragmentation \{$P_{f1}, \ldots, P_{fh}, C$\} of pattern $P(V_P, E_P)$, data graph $G(V, E)$, and pattern updates $\Delta P$.

@@

We use \fs to classify the match status of balls in $G$ into $2^h$ types \wrt ${\cal P}_h$.
For a ball with type code $(b_1,\ldots,b_h)$, $b_i$ is 1 iff $P_{fi}$ matches the ball via graph simulation.

@@

\ni (2) For balls linked with $tc$ $(1, 1)$, \eg ball $\ball{[\kw{PM_1},2]}$,
there are matches to both $P_{f1}$ and $P_{f2}$ in the ball.
Besides, there exist balls $\ball{[\kw{PM_2},2]}$, $\ball{[\kw{BA_3},2]}$ and $\ball{[\kw{PM_4},2]}$
linked with $tc$ $(1, 0)$, $(0, 1)$ and $(0, 0)$ respectively. 
%
For simplicity, we consider these 4 balls only in the sequel.
\end{example}

>>>>

Auxiliary structures fall into two classes:
maintain partial matches and handle pattern incremental computing. Consider an $h$-fragmentation ${\cal P}_h$ = \{$P_{f1}, \ldots, P_{fh}, C$\} of pattern $P(V_P, E_P)$, data graph $G(V, E)$, and pattern updates $\Delta P$.

@@

We use \fs to classify the match status of balls in $G$ into $2^h$ types $\wrt$ ${\cal P}_h$.
For a ball with type code $(b_1,\ldots,b_h)$, $b_i$ is 1 iff $P_{fi}$ matches the ball via graph simulation.

@@

\ni (2) For balls linked with $tc$ $(1, 1)$, \eg ball $\ball{[\kw{PM_1},2]}$,
there are matches to both $P_{f1}$ and $P_{f2}$ in the ball.
Besides, there exist balls $\ball{[\kw{PM_2},2]}$, $\ball{[\kw{BA_3},2]}$ and $\ball{[\kw{PM_4},2]}$
linked with $tc$ $(1, 0)$, $(0, 1)$ and $(0, 0)$ respectively.
%
For simplicity, we use these 4 balls only in the following analysis.
\end{example}
